---
title: "Sonify from PDB"
output: rmarkdown::html_vignette
author: Davide Provasi
vignette: >
  %\VignetteIndexEntry{Programming with dplyr}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}

---

```{r}
require(pdb2wave)
require(tidyverse)
```

## Read waves from DFT frequencies from SI of Yu, Chi-Hua, et al.ACS nano (2019).
```{r}
setwd("~/Desktop/protein_sounf")
wavpath = "FINAL SI/DFT BASED AA SOUNDS/"
aa_waves = get_aa_waves(wavpath)
```

## 5xdj example, and compare to MP3 file from Yu, Chi-Hua, et al.ACS nano (2019).
### Read sequence and secondary structure from csv file

```{r}
data_5xdj = get_structure_nopdb("5xdj.cc")
wave_stereo2 = gen_tune(data_5xdj$seq,data_5xdj$ses)
plot(wave_stereo2)
play(wave_stereo2,player = "afplay")
```

### Read mp3 file and compare
```{r}
wmp3 = tuneR::readMP3("FINAL SI/5xdj.mp3")
comp = tuneR::Wave(left=wmp3@left[1:239616], 
            right=wave_stereo2@right[1:239616],
            bit=16,samp.rate = 44100)
plot(comp)
play(comp, player = "afplay")
```

# mu-opioid receptor, from active structure, chain A
Calculate distances from right/left reference residues
to mimick sound localisation 

```{r}
data_5c1m = get_structure_pdb(
  "~/5c1m_a.pdb",
  refL_resno = 229,
  refR_resno = 315)

wave_stereo = gen_tune(
  data_5c1m$seq, 
  data_5c1m$ses, 
  distL = data_5c1m$distL, 
  distR = data_5c1m$distR)

plot(wave_stereo)
play(wave_stereo, player = "afplay")
tuneR::writeWave(wave_stereo, filename="5c1m.wav")
```

# mu-opioid receptor, from inactive structure, chain A
Calculate distances from right/left reference residues
to mimick sound localisation 
```{r}
data_4djh = get_structure_pdb("~/4djh_a.pdb",
                              refL_resno = 102, 
                              refR_resno = 236)

wave_stereo = gen_tune(
  data_4djh$seq, 
  data_4djh$ses, 
  distL = data_4djh$distL,
  distR = data_4djh$distR)

plot(wave_stereo)
play(wave_stereo, player = "afplay")
tuneR::writeWave(wave_stereo, filename="4djh.wav")


galpha = get_structure_pdb("~/3sn6_g.pdb",
                           refL_resno = 58, 
                           refR_resno = 231)

wave_stereo_ga = gen_tune(galpha$seq, galpha$ses, distL = galpha$distL,distR = galpha$distR)
plot(wave_stereo_ga)
play(wave_stereo_ga, player = "afplay")
```


